### 2014-03-02 paper/extensions.tex
privs

\paragraph{Labeled values}
\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}
\subsubsection{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
Hritcu:2013:YIB:2497621.2498098,myers:jif}) rely on privileges to
implement many applications.

Both the LIO and SWAPI implementations already support such features.
%
Extending our calculus to consider privileges
%
The challenge with such an extension, however, lies in the precise
security guarantees that must be proved.
%

>>>>

\paragraph{Labeled values}
\paragraph{Labeled references}
\paragraph{Labeled synchronization primitives}
\subsubsection{Privileges}
Decentralized IFC extends IFC with the decentralized label model of
Myers and Liskov~\cite{myers:dlm} to allow for more general
applications, including systems consisting of mutually distrustful
parties.  In a decentralized system, a computation is executed with a
set of \emph{privileges}, which, when exercised, allow the computation
to declassify data (e.g., by lowering the current label).
%
Practical IFC systems
(e.g.,~\cite{Zeldovich:2006, lio,
Hritcu:2013:YIB:2497621.2498098, myers:jif}) rely on privileges to
implement many applications.
%
Since both the LIO and SWAPI implementations already support such features,
we believe that extending our calculus to consider privileges is
straight forward.
%
However, the challenge with such an extension lies in the precise
security guarantees that must be proved.
%
Addressing this problem is a natural direction for this work.
